\cvsection{Projects \& Presentations}

\begin{bulletlist}
	\item \acentry{Covid19 Dashboard}{ (Python, Django)}{May 2020}
	\begin{bulletlist}
		\item[-] Developed a covid19 dashboard for Ahmedabad with Asst. Prof. Udit Bhatia and team.
		\item[-] Worked on road network calculation parallelizataion and code optimization. 
		\item[-] Designed and Deployed the Dashboard UI
	\end{bulletlist}
	\item \acentry{Email Parser}{ (Python, Stanford NLP API, Gmail API)}{Jan. 2019}
	\begin{bulletlist}
		\item[-] Tackled the Email Parsing problem in Hackathon at IIT Gandhinagar
		\item[-] Extracted detials of seminars, talks and workshops using NLP.
		\item[-] Presented a live demo of the same.
	\end{bulletlist}
	\item \acentry{Spell Check}{ (Python)}{Dec. 2018}
	\begin{bulletlist}
		\item[-] Attempted to use basic parameters like difference in absolute length to predict the correct spelling.
		\item[-] Determined the weight of each parameter and its powers using stochastic gradient descent
	\end{bulletlist}
	\item \acentry{Pattern Matching using FPGA }{(Verilog)}{Nov. 2018}
	\begin{bulletlist}
		\item[-] Objective was to find the number of overlapping occurences with given pattern and text.
		\item[-] Project was done using Vivado and implemented on Basys3 board.
		\item[-] Course Project for ES203 (Digital Systems - Prof. Joycee Mekie)
	\end{bulletlist}
	\item \acentry{Wi-fi Security}{}{Apr. 2018}
	\begin{bulletlist}
		\item[-] Attempted the Wi-fi security question in the Hackathon conducted at IIT Gandhinagar
		\item[-] Objective was to find security issues on the provided Wifi network
		\item[-] Discovered and gave a presentation on default credentials and telnet exploit (CVE-2017-3881)\\ security flaw with the network switch
	\end{bulletlist}
	\item \acentry{Wikiscrape }{(Python)}{Nov. 2017}
	\begin{bulletlist}
		\item[-] Objective was to scrape data from a given Wikipedia link
		\item[-] Used BeautifulSoup4 library for parsing HTML
		\item[-] Course Project for ES112 (Computing - Prof. Neeldhara Misra)
	\end{bulletlist}
	\item \acentry{Question Paper Generator }{(Python)}{Nov. 2017}
	\begin{bulletlist}
		\item[-] Authored a script to retrieve question data from airtable and create a question paper with user input conditions in LaTeX typesetting
		\item[-] Used the airtable API to retrieve the data and created a system get a random question set following the given constraints, and then output a question paper
		\item[-] Course Project for ES112 (Computing - Prof. Neeldhara Misra)
	\end{bulletlist}
	\item \acentry{Automail }{(Python)}{Jul. 2017}
	\begin{bulletlist}
		\item[-] Created an automatic mailing script which use database
		\item[-] Utilized raw SMTP for sending e-mails
	\end{bulletlist}
\end{bulletlist}